Final Model Analysis

### 2017-08-28 model fitting/final_model.Rmd
worked with survplot function

final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE, time.inc = 0.5, dxy = TRUE)

@@

##### Fitting the model to the full data set

@@

# using different function
pec::predictSurvProb(final, newdata = test1[1:3,], times = c(0.5, 1, 10))
```

@@

```{r}
# plots log hazard for each variable 
plots <- ggplot(Predict(final)) # output is messy, figure out how to access each plot separately

@@

# must specify a variable 
rms::survplot(final, ampm, time.inc = 100, col = 1:4, n.risk = TRUE)

# plot the effects of predictors
plot(Predict(final, new_category))
plot(Predict(final, new_user))
plot(Predict(final, new_user, new_category))

@@

```{r}
# input vector of times to predict on + data set to be used in predictions
# function runs really slow
# outputs matrix of predicted survival probabilities 
# sets up variables needed in the new data 
get_survival <- function(times, data) {
  # setting up necessary variables in new data 
  newdata <- oshitar::variable_setup(data)

  # imports data to build model on 
  x <- read.csv("final_data.csv", head = TRUE)
  # builds model 
  model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE)
  # gets survival probabilities 
  surv_probs <- pec::predictSurvProb(model, newdata = newdata, times)
  return(surv_probs)
}

>>>>

x$text_length2 <- x$text_length**2 # for future use
x$sqrt_tag_score <- sqrt(x$avg_tag_score)

final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE, time.inc = 0.5, dxy = TRUE)
final

@@

##### Assessing model fit on full data

* significant predictors (pvalues < 0.05):
    + new_category: Apple Product, Camera, game console, other, pc, vehicle
    + new_user
    + contain_unanswered
    + text_all_lower
    + update
    + prior_effort 
    + weekday: Thursday
    + avg_tag_score (sqrt)
    + spline on avg_tag_length
* Interpretations of signficant predictors
    + Apple Product: (beta = 0.93) log hazard of getting answered for apple products is 0.93 higher than for android/othe phones, controlling for other predictors. (HR = exp(beta) = 2.554) Hazard of getting answered is 155% higher for apple products compared to android/other phones, controlling for other predictors 
    + avg_tag_score (sqrt): (beta = 2.8764) log hazard of getting answered increases by 2.88 for every 1 unique increase in the square root of avg_tag_score, adjusting for other predictors. HR = 17.75, the hazard of getting answered increases by 167.5% for each one unit increase in the square root of the average tag score, adjusting for other predictors

@@

# using different function
pec::predictSurvProb(final, newdata = test1[1:3,], times = c(0.5, 1, 10))
# interpretation:
#   for question 380, the probability that it remains unanswered beyond 30 minutes is 0.53
#   for question 2195, the probability that it remains unanswered byond 30 minutes is 0.85
```

@@

```{r}
# plots log hazard for individual predictors 
ggplot(Predict(final, new_category))  
ggplot(Predict(final, device_length))
ggplot(Predict(final, text_length))
ggplot(Predict(final, avg_tag_length))
ggplot(Predict(final, newline_ratio))

@@

# must specify a variable 
rms::survplot(final, ampm, time.inc = 100, col = 1:4, n.risk = TRUE, xlab = "Hours")
rms::survplot(final, new_category, time.inc = 100, col = 1:length(levels(x$new_category)), xlab = "hour")
rms::survplot(final, new_user = 0, conf.int = .95, time.inc = 100) # can change variable it plots 
```

@@

```{r}
# input vector of times to predict on + data set to be used in predictions
# function runs really slow
# outputs matrix of predicted survival probabilities 
# sets up variables needed in the new data 
get_survival <- function(times, data) {
  # setting up necessary variables in new data 
  newdata <- oshitar::variable_setup(data)
  # imports data to build model on 
  x <- read.csv("final_data.csv", head = TRUE)
  # builds model 
  model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE)
  # gets survival probabilities 
  surv_probs <- pec::predictSurvProb(model, newdata = newdata, times)
  return(surv_probs)
}
